---
title: "IPWK13-CORE - PART 1"
author: "Elizabeth Josephine"
date: "11/04/2020"
output: github_document
---

# PROBLEM DEFINITION
## **a) Specifying the Question**

Determining which individuals are most likely to click on the ads of the Kenyan entrepreneur

## **b) Defining the metrics for success**

Bivariates and univariate Exploratory data analysis

## **c) Understanding the context**

Determination of the audience the entrepreneur can target

## **d) Recording the Experimental Design**

1.   Define the question, the metric for success, the context, experimental design taken.
2. Read and explore the given dataset.
3. Find and deal with outliers, anomalies, and missing data within the dataset.
4. Perform  univariate and bivariate analysis.
5. From your insights provide a conclusion and recommendation.
 
## **e) Relevance of the data**

The data used for this project is necessary for determining which audience should be targeted

[http://bit.ly/IPAdvertisingData].

# DATA ANALYSIS
## DATA SOURCING
```{R}
# loading libraries
library(relaimpo)
library(data.table)
library(ggplot2) # Data visualization
library(ggthemes) # Plot themes
library(plotly) # Interactive data visualizations
library(dplyr) # Data manipulation
library(psych) # Will be used for correlation visualization

```

```{R}
# importing our data
# reading our data
df <- fread('http://bit.ly/IPAdvertisingData')
df
```

## DATA CHECKING
```{R}
# previewing the dataset
View(df)

```

```{R}
# previewing the column names
colnames(df)

```

```{R}
# previewing the dataset
class(df)

```
```{R}
# previewing the datatypes of the dataset
sapply(df, class)
```

```{R}
# previewing the head of the dataset
head(df, n = 5)

```

```{R}
# previewing the tail of the dataset
tail(df, n = 5)

```

```{R}
# checking the structure of the data
str(df)

```

```{R}
# checking the dimension/shape of the data
dim(df) # 1000 rows and 10 columns
```

```{r}
# selecting needed columns
df <- subset(df, select = c("Daily Time Spent on Site", "Age", "Daily Internet Usage", "Male", "Country", "Clicked on Ad" ))
colnames(df)

```

## DATA CLEANING
### Missing Values
``` {r}
# checking for missing values
sum(is.na(df))# there are no missing values in the data
```

``` {r}
# displaying all rows from the dataset which don't contain any missing values 
na.omit(df)
```

### Duplicates

``` {r}
# checking for duplicates
duplicated_rows <- df[duplicated(df),]
duplicated_rows # there are no duplicates in the data
```

``` {r}
# showing these unique items and assigning to a variable unique_items below
unique_items <- df[!duplicated(df), ]
unique_items
```

``` {r}
# renaming columns for easy analysis
df <- df %>% rename(Daily_Time_Spent_on_Site = "Daily Time Spent on Site")
df <- df %>% rename(Daily_Internet_Usage = "Daily Internet Usage")
df <- df %>% rename(Clicked_on_Ad = "Clicked on Ad")

    
df
colnames(df)
```

### Checking for outliers

``` {r}
# visualizing any existing outliers using a boxplot
#df1 <- subset(df, select = c("Daily Time Spent on Site", "Age", "Daily Internet Usage", "Male", "Clicked on Ad"))

df1 <- df %>% select_if(is.numeric)
# df1
# %>%select(-c(Male, `Clicked on Ad`))

boxplot(df1)# there are no outliers in the data
```

```{R}
colnames(df)
```
# EXPLORATORY DATA ANALYSIS
## Univariate Analysis
### Measures of Central Tendency

``` {r}
# descriptive statistics
# these summaries will provide us with the measures of central tendencies of the numerical columns
describe(df1)
```

```{R}
# Finding the mode of age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

df.Age.mode <- getmode(df$Age)
df.Age.mode
```
### Measures of Dispersion
``` {R}
# Since we cannot find the measures of dispersion for all the six
# columns at a go, i will work with age and daily internet usage
```

```{R}
# Finding the minimum code
df.Daily_Internet_Usage.min <- min(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.min
```

```{R}
# Finding the minimum code
df.Age.min <- min(df$Age)
df.Age.min
```
```{R}
# Finding the maximum code
df.Daily_Internet_Usage.max <- max(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.max
```

```{R}
# Finding the maximum code
df.Age.max <- max(df$Age)
df.Age.max
```

```{R}
# Finding the range code
df.Daily_Internet_Usage.range <- range(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.range
```

```{R}
# Finding the range code
df.Age.range <- range(df$Age)
df.Age.range
```

```{R}
# Finding the quantile code
df.Daily_Internet_Usage.quantile <- quantile(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.quantile
```

```{R}
# Finding the quantile code
df.Age.quantile <- quantile(df$Age)
df.Age.quantile
```

```{R}
# Finding the variance code
df.Daily_Internet_Usage.variance <- var(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.variance
```

```{R}
# Finding the variance code
df.Age.variance <- var(df$Age)
df.Age.variance
```

```{R}
# Finding the standard deviation code
df.Daily_Internet_Usage.sd <- sd(df$Daily_Internet_Usage)
df.Daily_Internet_Usage.sd
```

```{R}
# Finding the standard deviation code
df.Age.sd <- sd(df$Age)
df.Age.sd
```

### Univariate Graphical

```{R}
# creating a boxplot graph for the variable all the numerical variables
boxplot(df1, ylab = 'frequency', main = 'boxplot for numerical variables')

```

```{R}
# fetching the columns
Clicked_on_Ad <- df1$Clicked_on_Ad

# fetching the frequency distribution
Clicked_on_Ad_frequency <- table(Clicked_on_Ad)

# plotting the bargraph
barplot(Clicked_on_Ad_frequency,  xlab = 'Clicked_on_Ad', ylab = 'frequency',  main = 'barplot on Clicked_on_Ad_frequency')
```

```{R}
# fetching the columns
Ages <- df1$Age

# fetching the frequency distribution
Age_frequency <- table(Ages)

# plotting the bargraph
barplot(Age_frequency, xlab = 'Age', ylab = 'frequency',  main = 'barplot on Age_frequency')
# most of the visitors to the site were aged 31 years old and 37 years old
```

```{R}
# fetching the columns
hist(df1$Daily_Internet_Usage)
```

```{R}
# fetching the columns
hist(df1$Age)
```

## Bivariate analysis
```{R}
# colnames(df1)
# assigning columns to variables
# Age<- df1$Age

# finding the covariance of the numerical variables in df1
cov(df1)

```

```{R}
# finding the correlation of numerical variables in df1
cor(df1)
```

### Graphical Techniques
```{R}
# finding the correlation matrix
library(corrplot)
#rquery.cormat(df1, type="full")
res <- cor(df1)
round(res, 2)
```

```{R}
# creating a scatterplot
# plot(Age, Daily_Internet_Usage, xlab="Age", ylab="Daily_Time_Spent_on_Site")

df$`Clicked_on_Ad` <- as.factor(df$`Clicked_on_Ad`)
ggplot(df, aes(x=`Daily_Time_Spent_on_Site`,y=`Daily_Internet_Usage`, color= `Clicked_on_Ad`)) + geom_point()
```

# IMPLEMENTATION OF THE SOLUTION 
## SUPERVISED LEARNING

```{R}
# REQUIREMENT:  create a supervised learning model to help identify which individuals are most likely to click on the ads in the blog.
## Packages Needed

library(tidyverse)
library(stringr)
library(tidytext)
library(randomForest)
library(rpart)
library(rpart.plot)
library(mice)
```

### SVM
```{R}
library(caret)
```

```{R}
str(df1)
```


```{R}
# training datasets
intrain <- createDataPartition(y = df1$Age, p= 0.8, list = FALSE)
training <- df1[intrain,]
head(training)
testing <- df1[-intrain,]
head(testing)
```

```{R}
# We check the dimensions of out training dataframe and testing dataframe
dim(training); 
dim(testing);
```

```{R}
# We then clean the data using the anyNA() method that checks for any null values.
anyNA(df1)
```

```{R}
# Then check the summary of our data by using the summary() function
summary(df1)

```
```{R}

# For example, the V14 variables, which is our target variable, it holds only 2 values, either 0 or 1.
# This should be a categorical variable. To convert these to categorical variables, we need to factorize them.
# The following code will convert the training data frame’s “V14” column to a factor variable.

training[["Age"]] = factor(training[["Age"]])

# Before we train our model we will need to control all the computational overheads. 
# We will implement this through the trainControl() method. 
# We are using setting number =10 and repeats =3

trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

svm_Linear <- train(Age ~., data = training, method = "svmLinear",
trControl=trctrl,
preProcess = c("center", "scale"),
tuneLength = 10)

# We can then check the result of our train() model as shown below
svm_Linear
```


```{R}
# We can use the predict() method for predicting results as shown below.
# We pass 2 arguements, our trained model and our testing data frame.
test_pred <- predict(svm_Linear, newdata = testing)
test_pred
```

```{R}
# Now checking for our accuracy of our model by using a confusion matrix
# confusionMatrix(table(test_pred, testing$Age))
```



### linear regression model
```{R}
# previewing the dataset
head(df1)
```
``` {R}
# predicting the daily time spent on the site by the users
# Applying the lm() function.
multiple_lm <- lm(Daily_Time_Spent_on_Site ~ ., df1)

# Generating the anova table
anova(multiple_lm)

# Then performing our prediction 
pred2 <- predict(multiple_lm, df1)

# Printing out our result
pred2
```

```{R}
##predicting the age of the individuals who click on the site
# Train the model using the training sets and check score
linear <- lm(Age ~ ., data=df1)
summary(linear)

#Predict Output
predicted = predict(linear, df1)
predicted
```

### A Decision tree model 
```{R}

# Load the party package. It will automatically load other
# dependent packages.
library(party)

# Print some records from data set df1.
head(df1)
```

```{R}

# Creating the input data frame.
input.dat <- df1

# Creating the tree.
  output.tree <- ctree( Daily_Internet_Usage ~ Age + Clicked_on_Ad + 
Daily_Time_Spent_on_Site, 
  data = input.dat)

# Plotting the tree.
plot(output.tree)
```


### NAIVE BAYES

```{R}

library(tidyverse)
library(ggplot2)
library(caret)#confusionMatrix
library(caretEnsemble)
library(psych)
library(Amelia)#missmap
library(mice) #mice
library(GGally) #ggpairs
library(rpart)
library(randomForest)
library(tidyverse)
```


```{R}
# describing the data
describe(df1)
head(df1)
```

```{R}
# We convert the output variable into a categorical variable
df1$Clicked_on_Ad <- factor(df1$Clicked_on_Ad)
df1$Clicked_on_Ad
```

```{R}
head(df1)
```

```{R}
# We then clean our dataset by setting zero values to NA's
# ---
# 
#df1[, 1:3][df[, 1:3] == 0] <- NA
```

```{R}
# We visualize our dataset by checking how many missing values
# ---
# 
missmap(df1)
```

```{R}
# We use mice package to predict missing values
#mice_mod <- mice(df1[, c("Daily_Time_Spent_on_Site", "Age", "Daily_Internet_Usage", "Male", "Clicked_on_Ad")], method='rf')
#mice_complete <- complete(mice_mod)

```

```{R}
# We transfer the predicted missing values into the main data set
#df1$Daily_Time_Spent_on_Site <- mice_complete$Daily_Time_Spent_on_Site
#df1$Age <- mice_complete$Age
#df1$Daily_Internet_Usage <- mice_complete$Daily_Internet_Usage
#df1$Male<- mice_complete$Male
#df1$Clicked_on_Ad <- mice_complete$Clicked_on_Ad
```

```{R}
# Now checking whether there are still many missing values
missmap(df1)
```

```{R}
colnames(df1)
```

```{R}
# Creating some visualisations to take a look at each variable
# ---
# Visualisation 1
# 
ggplot(df1, aes(Age, colour = Clicked_on_Ad)) +
geom_freqpoly(binwidth = 1) + labs(title="Age Distribution by time spent on site")
```

```{R}
# Visualisation 2
# ---
# 
c <- ggplot(df1, aes(x=Daily_Internet_Usage, fill=Clicked_on_Ad, color=Clicked_on_Ad)) +
geom_histogram(binwidth = 1) + labs(title="Pregnancy Distribution by time spent on site")
c + theme_bw()
```

```{R}
# Visualisation 3
 
P <- ggplot(df1, aes(x=Male, fill=Clicked_on_Ad, color=Clicked_on_Ad)) +
geom_histogram(binwidth = 1) + labs(title="BMI Distribution by time spent on site")
P + theme_bw()
```


```{R}
# Splitting data into training and test data sets
# ---
# 
indxTrain <- createDataPartition(y = df1$Clicked_on_Ad,p = 0.75,list = FALSE)
training <- df1[indxTrain,]
training
testing <- df1[-indxTrain,]
testing
```

```{R}
# Checking dimensions of the split

prop.table(table(df1$Clicked_on_Ad)) * 100
prop.table(table(training$Clicked_on_Ad)) * 100
prop.table(table(testing$Clicked_on_Ad)) * 100
```

```{R}
# Comparing the outcome of the training and testing phase
# ---
# Creating objects x which holds the predictor variables and y which holds the response variables
# ---
#
x = training[,-5]
y = training$Clicked_on_Ad
```

```{R}

# Loading our inbuilt e1071 package that holds the Naive Bayes function.
# ---
# 
library(e1071)
```

```{R}
# Now building our model 
# ---
# 
model = train(x,y,'nb',trControl=trainControl(method='cv',number=10))
```

```{R}
# Model Evalution
# ---
# Predicting our testing set
# 
Predict <- predict(model, newdata = testing)

# Getting the confusion matrix to see accuracy value and other parameter values
# ---
# 
confusionMatrix(Predict, testing$Clicked_on_Ad )
```

### KNN

```{R}
library(class) #knn
```

```{R}


```